%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Obulpathi's resume
%%   - based off work by Michael DeCorte
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%
%% The following code sets up the document formatting
%%

%this assumes that res_yy.sty is in path
\documentstyle[hyperref, overlapped, line]{resume}

\hypersetup{backref,pdfpagemode=Full,colorlinks=true,urlcolor=blue,backref}

\addtolength{\oddsidemargin}{-0.50in}
\addtolength{\voffset}{-0.50in}
\addtolength{\textwidth}{2.00in} \addtolength{\textheight}{1.50in}

\renewcommand{\namefont}{\LARGE\emph}

\newcommand{\tabitem}{~~\llap{\textbullet}~~}

%%
%% The following code defines some macros for terms which have raised font
%% (ie 4\fourth would result 4th with the 'th' raised (superscripted)
%%

\def\Cplusplus{{\rm C\raise.5ex\hbox{\small ++}}}
\def\CSharp{{\rm C\raise.5ex\hbox{\small \#}}}
% 'st' 'nd' 'rd' 'th' superscripts for numbers
\def\first{{\raise.5ex\hbox{\small st}}}
\def\second{{\raise.5ex\hbox{\small nd}}}
\def\third{{\raise.5ex\hbox{\small rd}}}
\def\fourth{{\raise.5ex\hbox{\small th}}}

%% starting the actual document

\begin{document}

%the name in big fonts at the top of resume
%this is left aligned
\name{Obulapathi N Challa}

%\normalsize
\large
%this is right aligned
\address{ \ \ \ \ \ \ \ \ Mobile: 352-410-3713 \ \ \ \ \ \ \ \ \ \ Email:\href{mailto:obulpathi@gmail.com}{obulpathi@gmail.com} \ \ \ \ \ \ \ \ \ Website: \url{www.obulpathi.com}}

\address{ \ \ \ \ \  \ \ \ GitHub: \url{www.github.com/obulpathi} \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ LinkedIn: \url{www.linkedin.com/in/obulpathi}}
%\address{ \ \ \ \ \  \ \ \ Address: 6005 State Bridge Rd \#708 Duluth, GA 30097}

\begin{resume}

%\section{\textsc{Employer}}
%Rackspace Inc. 3080 Premiere Pkwy \#115, Duluth, GA.
%\section{\textsc{Work Interest}}
%Big Data, Cloud Computing, Computer Networks, Security and Open Source.
%Cloud Computing, Wireless and Computer Networks, Mobile Computing and Open Source.
%Goolge: Cloud Computing, Computer Networks, Network Security, Programming.

% Professional Summary
\section{\textsc{Professional Summary}}
$\bullet$ Expertise and leadership in building products, teams and communities around Data, Data Science, Deep Learning, Cloud, Big Data, Internet of Things, and Open Source\\
$\bullet$ Experience and proven ability in attracting, retaining and empowering the best people and fostering teams and learning culture around them\\
$\bullet$ Ability to drive innovation in data organizations through MeetUps, Hackathons, Rapid Prototyping, Real-time Analytics and A/B Testing\\
$\bullet$ A decade of experience in Data Science, Cloud Computing, Big Data, IoT, Deep Learning\\
$\bullet$ Experience around increasing product velocity by streamlining Agile practices like SCRUM, Kanban, CICD, Automated Testing and DevOps


% Skills
\section{\textsc{Business Expertise}}
{\bf Management:} Highly experienced with managing people, software projects and systems. Well versed with modern aglie software management practices including Agile, Kanban, Scrum, JIRA, CICD, DevOps, Automated testing, and Incremental Delivery. Expertise in understanding the complex and reducing risk while delivering software at high velocity.\\
{\bf Hiring:} Experience in recruiting, training, and managing IT staff. Well versed with hiring people with the skills needed to operate and support a wide range of IT divisions, including Deep Learning, Data Science, Cloud Computing, Big Data, Internet of Things, Data Center Operations and Software Development. Performed salary administration and conducting interviews and made recommendations for new hires, consultants and replacement personnel.\\
{\bf Budgeting and Cost Control:} Experience in taking the business needs, translating them into requirements in terms of people, software and hardware and boiling them into budget estimates and plans. Experienced with controlling or reducing costs while maintaining a high level of service to users, whenever possible. Performed several initiatives to identify and recommend new technology solutions that were targeted towards cost savings.\\
{\bf Vendor Relationship Management:} Participated in several hardware and software evaluations and maintained vendor contracts. Well versed with identifying and evaluating new tools/technologies to enhance functionality. Experienced with RFI, RFQ, and RFP processes. Also worked with business systems documentation, workflow analysis/process, and re-engineering.\\
{\bf Innovation:} Expertise in several innovation driving initiatives such as Hackathons, MeetUps, Tech Talks and Tech Crews. Created and organized several MeetUp groups on Deep Learning, Data Science, Cloud and Big Data. Conducted various educational programs for training on variety of topics including TensorFlow, Docker, Kubernetes, NoOps, DevOps, Hadoop, Spark and more. Organized company wide internal tech-talks for knowledge sharing. 
    
% Skills
\section{\textsc{Technical Skills}}
{\bf Data Science:} Machine Learning, Neural Networks, Deep Learning, OpenNLP, NLTK, Pandas, Scikit, DataFrame, Jupyter, TensorFlow, Tableau \\
{\bf Cloud:} Amazon AWS, Google Cloud, OpenStack, Containers, Docker, Kubernetese \\
{\bf Big Data:} Spark, Flink, Druid, Hadoop, Pig, Hive, Redshift, BigQuery, Dataflow \\
%{\bf Databases:} NoSQL, Cassandra, MongoDB, Redis, GraphX, Neo4j, MySQL, Postgres \\
{\bf IoT:} Atmel AVR, ARM, Edison, DSP, Flash, EEPROM, Sensors, I2C, SPI, USART, CAN \\
{\bf Analytics:} Amazon AWS, Google Cloud, OpenStack, Kubernetese

%{\bf Expertise:} Data Science, Cloud Computing, Big Data, Distributed Systems, REST APIs\\
%{\bf Software:} Python, Go, Java, Scala, C, C++, Bash, R, Julia, HTML, Linux and UNIX\\
%{\bf DevOps:} Ansible, Chef, Deployment Manager, CloudFormation, HEAT, Docker, CoreOS\\
%{\bf Web Stack:} Flask, Bottle, Twisted, Jinja, Django, Spring, Hibernate, Play, Jinja, Werkzeug\\
%{\bf Messaging:} Kafka, RabbitMQ, ZeroMQ, PubSub, SQS, Zaqar, Celery, Taskflow, Task Queue\\
%{\bf Security:} Kerberos, TLS/SSL, AD/LDAP, Bitcoin, Blockchain, Metaspoilt, Nmap\\
%{\bf Others:} Hiring, Git, Android, Akka, ZooKeeper, CDN, DNS, Vim, Bootstrap, IntelliJ IDEA, Google Apps, Microservices, Containers, Scalability, High Availability, Small Satellites, Drones, Robotics

%$\bullet$ 10 years of experience in software development using Python, Java and C\\
%$\bullet$ Expertise in Deep Learning, Machine Learning, Natural Language Processing, Image \& Speech Recognition, TensorFlow, SparkML, Scikit and Pandas.\\
%$\bullet$ Expertise in Amazon AWS, Google Cloud, OpenStack, Containers, Cloud Automation\\
%$\bullet$ Expertise in Spark, Hadoop, Pig, Hive, Cassandra, MongoDB, Redis, Kafka, Akka, Zookeeper\\
%$\bullet$ Expertise on batch as well as real time stream processing and analytics projects\\


\section{\textsc{Education}}
\textbf{PhD in Big Data and Cloud Computing from University of Florida} \hfill 2013 \\
Dissertation: CubeSat Cloud, a framework for distributed storage, processing and communication of remote sensing data on CubeSat Satellite clusters\\ \\
%\newline
\textbf{Masters in Electrical and Computer Engineering from University of Florida} \hfill 2010 \\
%\newline
\textbf{Bachelors in Information and Communication Technology from DA-IICT} \hfill 2007

%% the meat of the resume starts now
\begin{formatb}
  \employer{l}\dates{r}\\
%  \location{l}\\
  \body\\
\end{formatb}

\section{\textsc{Experience}}
\textbf{BI Big Data Expert at Nike} \hfill June 2016 - Present\\
Designed and built state-of-the-art data science platform using TensorFlow, Jupyter and Kubernetes on Google Cloud. Designed and built real-time streaming platform on AWS for capturing user activity using Kinesis Firehose, Kinesis Stream and Kinesis Analytics.\\
\textbf{Big Data Cloud Analytics Developer IV at Monsanto} \hfill Aug 2015 - Present\\
Designed and built state-of-the-art data science platform using Jupyter, Kubernetes on Google Cloud. Architected the data pipeline that ingest hundreds of billions of messages into Kafka and synchronizes in-house Read/Write Oracle Exadata cluster with Read-only Postgres in AWS. Architected and built enterprise DataHub platform consisting of Spark and Hadoop on AWS.\\
\textbf{Software Developer II at Rackspace Inc.} \hfill Mar 2014 - Aug 2015\\
Engineered OpenStack Poppy (CDN as a Service) and OpenStack Zaqar (Queuing system). Designed and developed solutions for log management, batch processing, real-time streaming and analytics using Spark, Hadoop, Pig Latin and Hive. Designed and built highly available and scalable web applications using Cassandra, MongoDB, Redis, Worker/Queue mechanisms.\\
\textbf{Software Development Engineer at Amazon AWS} \hfill May 2013 - Aug 2013\\
Designed and developed transport mechanism for synchronizing database replicas. Implemented asynchronous APIs for record transportation based on C++ Boost and Google ProtoBuffers. Automated the AWS infrastructure for managed MySQL at Amazon using CloudFormation.\\
\textbf{MAC Protocol Developer at xG Technology} \hfill Sep 2011 - Dec 2011\\
\textbf{Radio Software Integration Intern at BlackBerry} \hfill May 2011 - Aug 2011\\
\textbf{Research/Teaching Assistant at University of Florida} \hfill Jan 2009 - April 2013\\
\textbf{Research/Teaching Assistant, Research Engineer at DA-IICT} \hfill Aug 2006 - May 2008

\begin{formatb}
  \employer{l}\dates{r}\\
  \body\\
\end{formatb}

\section{\textsc{Projects}}
\textbf{OpenStack Poppy and OpenStack Zaqar} \hfill 2014 - 2015\\
Core contributor to OpenStack Poppy and OpenStack Zaqar. Engineered significant portion of their APIs. Designed and implemented several scalability and high availability mechanisms. Built POCs and implemented log management, analytics, billing, streaming analysis solutions.\\
\textbf{Bitcoinpy, Reversecoin and Blockchain analysis} \hfill 2013 - Present\\
Created Bitcoinpy, a Python implementation of Bitcoin with focus on hackability and modularity. Created Reversecoin, the worlds first cryptocurrency with reversible transactions. Performed statistical analysis of Blockchain using Python Pandas.\\
\textbf{CubeSat Cloud} \hfill 2010 - 2014 \\
Designed and implemented ``CubeSat Cloud", a framework for distributed storage, processing and communication of remote sensing data using CubeSat Distributed File System (inspired by HDFS), CubeSat MapReduce (like MapReduce) and CubeSat Torrent (inspired by Torrent) respectively. Code was written in Python Twisted and ran on a cluster of Raspberry Pis.\\
\textbf{FUNSAT V \& VI and SwampSat} \hfill 2008, 2009 \\
Lead UF's Small Satellite LASER Communication subsystems team in FUNSAT V and FUNSAT VI; Bagged first prize in FUNSAT-V satellite design competition held by NASA. Designed communication protocols for SwampSat. Designed and developed SwampSat cloud application, a distributed packet collector, decoder and analyzer in Python on App Engine.\\
\textbf{CENSE, WildCENSE and SmallCENSE} \hfill 2006 - 2008\\
Designed and developed CENSE, a delay tolerant WSN testbed for monitoring the habitat of wildlife. Developed WCFFS flash file system and wrote several device drivers. Developed and implemented a grid based localization technique using signal strength from radio base stations.\\
\textbf{Built a Custom Linux from scratch} \hfill 2005

%%
%% This section could also use more formatting, but looks ok, as is
%%

%\section{\textsc{Qualifications}}

%\emph{Programming Languages}: \Cplusplus, \CSharp, Cg, HLSL, ARB assembly, SML, OCaML, PHP, MySQL, Java, Python, Perl, MIPS assembly

%\emph{Libraries and Tools}: Vim, STL, DirectX, OpenGL, \LaTeX, GIMP, Adobe Suite, Macromedia Suite, MatLab, Mathematica, Microsoft Visual Studio, GCC, GDB


%%
%% Note that we're redefining the formatting
%% We only have one row of information now, instead of two
%%

\section{\textsc{Leadership \& Activities}}
%\textbf{Activity} \hfill Duration \\
%Description of Activity\\
\textbf{Organizer for Deep Learning Group \& Hackathons at Nike} \hfill 2016 - Present\\
\textbf{Organizer for Cloud and Big Data \& Google Developer Groups} \hfill 2014 - Present\\
\textbf{Tech Talk Organizer and TechCrew member at Rackspace} \hfill 2014 - 2015\\

%% Leadership Part
%\section{\textsc{Leadership}}
%\textbf{Activity} \hfill Duration \\
%Description of Activity\\
%\textbf{GatorLUG University of Florida Student Branch President} \hfill Fall 2009 - Present \\
%Established and lead the local Linux Users Group(LUG) at UF.\\
%\textbf{FUNSAT V, VI} \hfill Fall 2008, Fall 2009 \\
%Lead the Laser Communication subsystem design; Bagged first prize in FUNSAT-V satellite design competition held by NASA. Communications lead in FUNSAT VI.

% Publications
%\section{\textsc{Publications}}
%Enhancing Small Satellite Communication using Helical Antenna.
%\\GPS-less small turtle tracking using sensor networks.

%\begin{formatb}
%  \employer{l}\dates{r}\\
%  \body\\
%\end{formatb}
%
%\employer{\textbf{Software}}
%\dates{}
%\begin{position}
%Python, C, C++, Java, BASH, VIM, Bzr, GCC, GDB, Linux, UNIX.
%\end{position}
%
%\employer{\textbf{Hardware}}
%\dates{}
%\begin{position}
%AVR, MSP430, PIC, Various sensors, ...
%\end{position}

%%
%% Nothing special here, just a normal table
%%

%\section{\textsc{Course Work}}
%  \begin{tabular}{lllll}
%  Information Networks   & \ \ & Machine Learning    & \ \ & Theory of Computation \\
%  Computer Graphics      & \ \ & Machine Vision      & \ \ & Programming Languages \\
%  Software Engineering   & \ \ & Algorithms          & \ \ & Artificial Intelligence     \\
%  Operating Systems      & \ \ & Databases           & \ \ & Computer Architecture \\
%  Numerical Methods      & \ \ & Graph Theory        & \ \ & Differential Equations      \\
%  Probability Theory     & \ \ & Number Theory       & \ \ & Differential Geometry       \\
%  Advanced Calculus      & \ \ & Abstract Algebra    & \ \ & Advanced Combinatorics   \\
%  \end{tabular}


\end{resume}
\end{document}
